---
title: "Polish adaptive CDIs validation pilot"
format: html
---


```{r}
#| label: setup
#| include: false

# renv::init()
# devtools::install_github("gkrajewski/Multilada")

library(tidyverse)
library(Multilada)
```


## Data preparation

For the time being and for the sake of simplicity we get the demo data (age, sex, person filling in,
i.e., submitter) from the adaptive submissions only.
There will most likely be discrepancies and we may want to look at them at some point.
Also, checking the same vs different submitter mighht be interesting.

Also we take start date as the submission date (that's how it's been implemented so far),
but end date might be more accurate.

```{r}
#| label: prepare_ws

cdi_read("cdi", "ws_pl") -> ws_responses

# Cut off early test submissions (otherwise they throw errors):
ws_responses %>% filter(start_date > "2021-07-07") -> ws_responses

# Calculate sums:
cdi_count_oneCheckboxGroup(ws_responses, "word") %>%
     select(! type) %>% rename(score = n) -> ws_scores

# Get CAT data:
cdi_read("cdi", "ws-cat_pl_adaptive") -> ws_cat_responses
cdi_adaptive(ws_cat_responses) -> ws_cat_results
inner_join(ws_cat_results, ws_scores, by = "id") -> ws_comparisons
```

Seems like there are multiple entries for the same ID.
Should be cleaned...

**Better check the procedure below:**

For WG comprehension scores we add **U** sums and **P** sums
and subtract *both* sums. This way we include both those who checked **U**
for understanding and those who checked **P** only for understanding and
production, without counting twice those who checked both **U** and **P**.

```{r}
#| label: prepare_wg

cdi_read("cdi", "wg_pl") -> wg_responses

# Cut off early test submissions (otherwise they throw errors):
wg_responses %>% filter(start_date > "2021-07-07") -> wg_responses

# Calculate sums:
cdi_count_manyCheckboxGroups(wg_responses, "word", answer = "first") %>%
     rename(U_score = n) %>% select(id, end_date, U_score) -> wg_u_scores
cdi_count_manyCheckboxGroups(wg_responses, "word", answer = "second") %>%
     rename(score = n) %>% select(id, end_date, score) -> wg_p_scores
cdi_count_manyCheckboxGroups(wg_responses, "word", answer = "both") %>%
     rename(both_score = n) %>% select(id, end_date, both_score) %>%
     full_join(wg_u_scores) %>% full_join(wg_p_scores) %>%
     mutate(score = U_score + score - both_score) %>%
     select(id, end_date, score) -> wg_u_scores

# Get CAT data:
cdi_read("cdi", "wg-cat_pl_adaptive") -> wg_cat_responses
cdi_adaptive(wg_cat_responses) -> wg_cat_results

wg_cat_results %>% filter(group == "rozumienie") %>%
     inner_join(wg_u_scores, by = "id") -> wg_u_comparisons
wg_cat_results %>% filter(group == "mowa") %>%
     inner_join(wg_p_scores, by = "id") -> wg_p_comparisons
```

Seems like there are multiple entries for the same ID.
Should be cleaned...

Also, the number of IDs with both *full* and *adaptive* submissions is surprisingly low.
